---
title: "LIve Session 2 CLT"
author: "Bivin"
date: "9/6/2018"
output:
  html_document:
    df_print: paged
---
```{r}
 
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simulator to Demonstrate CLT

## Control Parameters

From the Rmarkdown file in the Live Session 1 repository on Github, we create an R file by placing the extension *.r instead of the *.Rmd extension.  From here, we can modify and debug the assignment.  

Restated, the assignment is:  
1. Adapt the code to generate a population of 10,000,000 from a chi-square distribution with 2 degrees of freedom.  This is a heavily right skewed 
distribution.  (Hint: rchisq()) You will have to red up on this function and probably do some trial and error.  Being able to learn new functions and methods is a key skill.

```{r}
set.seed(0)

n1 <- 10000000

#generate 10,000,000 random values that follow Chi-Square distribution with df=2
values <- rchisq(n1, df = 2)

#view first 5 values
head(values)

#create a histogram to visualize distribution of values
hist(values, col = "green", main = paste("Distribution of the Chi-Square population: n = ", n1), xlab = "Dist 1 Chi-Square", xlim = c(-15,15))

#Determine the mean and standard error of the values
x <- mean(values)
y <- sd(values)
paste("The mean of the population is,", x, "The standard deviation of the population is,", y)
z <- (x - y)

paste("The difference between the mean x and the standard deviation y is,", z)
```

## Part 4 is the question: "According to CLT, what should be the approximate
#distribution of sample means of size 50 from this right skewed population?

#ANSWER:  The means of the sample size 50 should be the same as the mean of the population:  mux = mu(sample)

#What shoud be the mean and standard error of the mean (stand deviation of of the distribution of sample means)?
#ANSWER: The standard error should be smaller by a facter of 1/squareroot(50)

#Part 5 is to run the math and check the CLT

##SECOND PART

```{r}
n2 <- 50 # sample size per sample for 1st distribution
simulations <- 10000 #number of samples and thus number of xbars we will generate.  
mu <- 0 # mean parameter for use with normal distribuions
sigma <- 1 # standard deviation parameter for use with normal distributions

xbar_holder1 <- numeric(simulations) # This will hold all the sample means for the first distribution.

for (i in 1:simulations)
{ 
 sample1 <- rnorm(n2,mean = mu, sd = sigma)

xbar1 <- mean(sample1)
xbar_holder1[i] <- xbar1
}

hist(xbar_holder1, col = "blue", main = paste("Distribution of the sample mean: n = ", n2), xlab = "Dist 1 Sample Means", xlim = c(-4,4))

summary(xbar_holder1) #5 number summary and the mean
sd(xbar_holder1) # standard deviation of dstribuion 1

paste(summary(xbar_holder1))
paste(sd(xbar_holder1))
```

